The first high-redshift changing-look quasars

### 2020-07-29 tex/MNRAS_submission/rv1/reply2referee.txt

		We thank the Reviewer and Scientific Editor for their
		comments and suggestions.  In particular we thank the
		Reviewer for a deep reading and thoughtful digestion
		of the manuscript, which has improved the paper.

@@

      	  We agree with this comment and to help the reader, in Table 1 we have removed the confusing ``Ionization Potential'' column,
	  while adding a column to the table noting the "Production Mechanism'' of each emission line.
	  We have a strong preference to retain this table, but leave it as a decision to the Editor as to whether to do so.

2. CLQ Selection and Line Measurements

(a) In section 2.2, the authors describe how they selected the initial candidates using the CRTS light curves. I would recommend some additional explanations and clarifications of the selection process, as follows.

(i) I recommend expanding on the the sentence "This allowed us to predict the photometric magnitudes at the epochs of the SDSS spectra for each source." I presume that the damped random walk model was used to INTERPOLATE between adjacent points in the light curve. If so, it would be useful to state that explicitly. It would also be useful to note the uncertainty in this interpolation scheme; this uncertainty is important in developing a criterion for what is an outlier, as the authors do. I would recommend elaborating on this matter by explaining why the specific criterion of |DV| > 0.3 was adopted (by the way, what are the units? magnitudes?).

@@

(iii) Finally, I would suggest noting how many quasars were selected for visual inspection by the automatic algorithm before the three final candidates were identified.

        Text has been added here for additional explanation.

(b) Figure 1. -- I found this figure to be rather busy, packed with information, and difficult to read. I would recommend breaking it up into two separate figures, one including the light curves and one including the spectra. In the process of doing so, I would recommend that the authors write the names of the quasars in the corresponding panels and make the fonts considerably larger so that the labels are easier to read (especially the fonts in the sub-panels that zoom in on specific emission lines).

	 As suggested, we have split the light curve and spectral figures up, increased the size of the fonts,
         and have written the names of the quasars in the appropriate panels.

@@

(c) At the very end of section 2.3 the authors note that they use photometric measurements to set the absolute scale of the non-SDSS spectra. It would be useful to note here the resulting uncertainty in flux calibration and whether this uncertainty was propagated into measurements of the continuum and emission lines from these spectra.

           A sentence has been added here.

(d) Table 3. -- This is an important table because it includes a great deal of useful information for the three high-z CLQs but it can be presented much better. I give here detailed recommendations about this table which are connected to and may duplicate comments I make in other parts of this report. - I would recommend including in the text (perhaps in section 2.4) a brief discussion of how the uncertainties in the measured quantities were determined. If these uncertainties are estimated by QSfit, it would suffice to explain very briefly how that is done and refer the reader to the paper that described that code.

	 We have added a paragraph at the end of Section 2.4 detailing how
	 the uncertainties in the spectral line quantities were determined.

@@

(b) In the first paragraph of section 3.2 the authors note that they set E(B-V)=0 in the fitting process. Is this the reddening intrinsic to the quasar or does it also include the reddening in the Milky Way? I presume the latter is known and could (and should) be corrected.

       We have updated the results (Table 3) and figures (Figs 5, 6
       and 7) obtained by taking the Milky way extinction values for
       the three objects into account.

(c) Equation (1) in section 3.3. -- This equation, as written, appears to be wrong because the LHS is a log while the RHS is not and there should be constants or calibration factors to connect the black hole mass to the luminosity and FWHM combination. Moreover, the exponent of the luminosity is not exactly 0.5 according to empirical determinations. I would very strongly recommend that the authors correct this equation and revise the relevant discussion. Section 3.7 of the paper by Shen et al. (2011, cited just before equation 1) includes a detailed discussion of the calibration of this relation and several references to the original papers that report the calibration factors. I recommend that the authors begin by consulting that paper and then tracking down the most up-to-date calibration of equation (1), which should be the most appropriate calibration to use here (section 4 of Grier et al. 2019, ApJ, 887, 38 would be a good place to start in order to find the most up-to-date calibrations). The revised text should include appropriate references to the original papers reporting the calibration adopted by the authors.

   	Yes, this is an excellent point.
	We have (significantly) updated and corrected the equation and
	revised the relevant discussion, adding key text and recent 
	references here.

### 2020-07-29 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
almost there...

      {\bf The physical mechanism for the generation of the emission lines
        e.g., full ionization, collisionally excitation (``Collisional Ex.'' in the rable) or recombination are also given in

@@

While there have been many studies on triply ionised carbon, i.e.,
\civ, these have tended to focus on broad absorption line quasars
\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
\citep{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}. As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: {\it (i)} the {\it
global} (or {\it ensemble}) Baldwin effect, which is an
anti-correlation between the emission line equivalent width and the
underlying continuum luminosity of single-epoch observations of
a large number of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an individual, variable 
AGN \citep{PoggePeterson1992}. The ensemble and intrinsic Baldwin effect 
has been observed in the \civ\ broad absorption line quasar population,
However, dramatic changes in the 
collisionally excited broad {\it emission} line of \civ\ --- and
indeed \ciii\ --- have not to this point been reported.

@@

{\bf 
 Most of the strong lines in the rest-frame near-UV spectrum of quasars are
collisionally excited, including C\,{\sc iii}, C\,{\sc iv} and N\,{\sc
v}.  The \heii~$\lambda$1640 recombination line is among the exceptions.

Photoionization followed by recombination determines the ionization
level of carbon, and collisional excitation from the ions ground level 
determines the line intensity. Other processes do happen,
(including radiative and three body recombination to the upper levels 
of the transition), but they are much slower unless the density is
extremely high \citep[e.g., ][and H. Netzer,
priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply ionised,
\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
}
%%
Details of the atomic transitions and physical mechanisms that produce
strong rest-frame UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CLQ Selection and Line Measurements}
{\bf A statistical search using optical light curves to initiate spectroscopic follow-up
  observations is proving an efficient CLQ finder, and by design
our data sources and overall methodology, are in common to the recent
\citet{Ross2018}, \citet{Stern2018} and \citet{Graham2020} papers.
}
%
In this section we present the photometric data used to select the
CLQs and give details of the multiwavelength data where we have it.
{\bf We use data from the Catalina Real-time Transient Survey, PanSTARRS,
  the Zwicky Transient Facility, the WISE mission and SDSS.}
We then give details of the spectroscopic data including emission
lines measurements.

\subsection{Photometry}
\subsubsection{Optical Photometry}
We use optical data from the Catalina Real-time Transient Survey
\citep[CRTS;][]{Drake2009, Mahabal2011}, the Panoramic Survey
Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
Stubbs2010, Tonry2012, Magnier2013}, and the Zwicky Transient Facility
\citep[ZTF;][]{Bellm2019_ZTFOverview}.

The CRTS archive\footnote{http://catalinadata.org} contains the
Catalina Sky Survey data streams from three telescopes -- the 0.7-m
Catalina Sky Survey (CSS) Schmidt and 1.5-m Mount Lemmon Survey (MLS)
telescopes in Arizona, and the 0.5-m Siding Springs Survey (SSS)
Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
with four exposures per visit, separated by 10 min. The survey observes
over 21 nights per lunation. The data are broadly calibrated to
Johnson $V$ \citep[for details, see][]{Drake2013} and the current CRTS
data set contains time series for approximately 400 million sources to
$V \sim 20$ above Declination $\delta > -30$deg from 2003 to 2016 May (observed with CSS
and MLS) and 100 million sources to $V \sim 19$ in the Southern sky
from 2005 to 2013 (from SSS). CRTS has been extensively used to study 
quasar variability \citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature,
Graham2017, Graham2020, Stern2017, Stern2018, Ross2018}.

@@

The Zwicky Transient Facility (ZTF; http://ztf.caltech.edu) is a new
robotic time-domain sky survey capable of visiting the entire visible
sky north of $-$30 deg declination every night. ZTF observes the sky in
the $g$, $r$, and $i$-bands at different cadences depending on the
scientific program and sky region \citep{Bellm2019_ZTFSurveys,
Graham2019_ZTF}. The ZTF 576 megapixel camera with a 47 deg$^{2}$
field of view, installed on the Samuel Oschin 48-inch Schmidt
telescope at Palomar observatory, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30-sec exposure during new moon \citep{Masci2019}.
\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
  {figures/J1205+3422_landscape_LC.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
  {figures/J1638+2827_landscape_LC.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.20cm 0.1cm, clip]
  {figures/J2228+2201_landscape_LC.png}
  \vspace{-6pt}
  \caption[]{The light curves for the three high-redshift CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
    The timing of the spectral observations are indicated with vertical dashed lines.}
  \label{fig:civ_clqs_LCs}
\end{figure*}

\subsubsection{Mid-Infrared Photometry}
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
of the {\it WISE} mission \citep[2010 January; ][]{Wright2010} through
the fifth-year of {\it NEOWISE-R} operations \citep[2018 December;
][]{Mainzer2011}. The {\it WISE} scan pattern leads to coverage of the
full-sky approximately once every six months (a ``sky pass''), albeit
it with a gab between 2011 February and 2013 October when the
satellite was placed in hibernation. Hence, our light curves have a
cadence of 6 months with a 32-month sampling gap.

@@

\subsection{CLQ Selection}
{\bf As this is the first time high-redshift CLQs have been studied,
defining a formal and automatic process is not an trivial task.  Hence
we focused on a method and threshold which selects the most promising
candidates, with no claim of completeness, in a number suitable to be
inspected visually.}

Our high-redshift CLQs were identified as follows.  We selected all
64,774 SDSS DR15 sources with $z > 0.35$ classified as `quasar', that
had at least two spectra separated by $\geq 100$ days, and that had a
corresponding CRTS light curve. We fitted a damped random walk to the
CRTS data via Gaussian process regression (using the
\href{https://gpy.readthedocs.io/en/deploy/}{GPy Python} library).
{\bf This allowed us to predict the photometric magnitudes and their
uncertainties at the epochs of the SDSS spectra for each source
\citep[see][]{Rasmussen_Williams2006}.}
%%
Candidate objects with $|\Delta V| > 0.3$ magnitude were then selected
for visual inspection, {\bf looking for at least a 33\% change in flux
between the two epochs. Approximately 1\% of quasars should show this
level of significant variability over the timescales considered
\citep{Graham2017}.}

@@

Proper comparison of the spectra requires reliable flux calibrations,
which is a challenge since not all data were taken in photometric
conditions.  SDSS spectra are spectrophotometrically calibrated.  BOSS
and eBOSS spectra have spectrophotometric corrections applied in the
latest data release \citep{Hutchinson2016, Jensen2016, Margala2016}.
However, some of the Palomar and Keck data suffered from variable
conditions and clouds.  For lower redshift AGN, the narrow \oiii
emission line is typically used to align spectrophotometry since it is
spatially extended and not expected to change significantly on human
timescales \citep[e.g.,][]{Barth2011}. However, due to the
high-redshift of our quasars, \oiii is not available to us to use for
scaling the spectra.  Instead, we use photometric data from the ZTF
since our Palomar and Keck data were all taken after MJD 57500.  This
provides broad-band photometry at the time of the spectroscopy, which
we use to scale the spectra whose initial calibration is based on
spectrophotometric standards observed on the same nights.  {\bf We
note the resulting uncertainty in flux calibration is 2-5\%.  This
uncertainty is not propagated into measurements.}

@@

In particular, we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and EWs of 20 emission
lines, including \civ, \ciii, and {Mg\,{\sc ii}}. We process and fit
all nine spectra (3 quasars with 3 epochs) using the lastest version
(v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, as is the case for all
our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.

{\bf As described in \citet{Calderone2017}, the uncertainties in the
measured quantities are determined by two methods; a Fisher matrix
method and a Monte Carlo resampling method.  One might expect
correlations among model parameters, e.g. emission-line luminosities
and widths, and thus the Fisher matrix method to underestimates the
errors.  However, upon investigation, the parameters of the involved
model components (a power-law for the continuum, and a single
Lorentzian profile for the emission lines) show negligible
correlations, hence we use the Fisher matrix method to estimate the
uncertainties on the model parameters.  Section 2.8.3 and Appendix B4
of \citet{Calderone2017} gives further details and compares the Fisher
matrix and Monte Carlo resampling uncertainties and distributions.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
curves for three high-redshift CLQ quasars.

Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for
SDSS J1205+3422.  For J1205+3422, our spectral observations cover 5195
observed days, corresponding to 1691 days in the rest-frame. This
quasar was initially identified in SDSS in 2005 May as a bright, $g
\approx 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv},
\civ, C\,{\sc iii}, and Mg\,{\sc ii}.  \civ\ has a blueshift of
$\approx$580$\pm$80 km s$^{-1}$.  By 2019, however, the optical
brightness dropped by nearly 2 magnitudes and the spectra are
significantly less blue.  \lya and \nv are detectable in both 2019
spectra, but is just blueward of the wavelength range covered by the
original SDSS spectrum. The \civ\ and \ciii\ lines have faded
significantly between the SDSS observation in 2005 and the Palomar
observations in 2019.  Note that \civ\ is extremely faint in the 2019
February spectrum, but that night suffered from poor conditions.

Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for
SDSS J1638+2827.  For J1638+2827, our spectral observations cover 4030
observed days, corresponding to 1265 days in the rest-frame. Here, in
the initial epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
\ciii\ emission lines have faded, the continuum slope around 1400\AA\
has changed from $\approx-1.16$ to $\approx-2.17$, but the \lya/\nv
emission complex is very similar in shape {\bf and intensity}. Around
870 days in the rest-frame after the second spectral epoch, at the
time of the third spectral epoch, the source has brightened from
optical magnitudes of $\sim$20 mag to $\sim$18.5 mag. Ly$\alpha$,
N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
\mgii\ being seen for the first time at high signal-to-noise. An
absorption feature between \lya and \nv is seen in all three spectral
epochs.

Figure~\ref{fig:civ_clqs_J22_spec} shows the rest-frame spectra for
SDSS J2228+2201.  For J2228+2201, our spectral observations cover 2504
observed days, corresponding to 778 days in the rest-frame. Over the
course of 240 rest-frame days, \civ\ and \ciii\ both {\it emerge} as
BELs and {\bf the standard UV/blue continuum becomes stronger.}  Then,
over the course of 538 days in the rest-frame, the broad emission,
while still very present, reduces in line flux the UV/blue continuum
diminishes.  However, the third epoch still corresponds to a source
more luminous than the initial BOSS spectrum.

\begin{figure*}
  \centering
  \includegraphics[width=18.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit models of the \civ\ spectral region.
    The solid blue line is the Lorentzian profile fit to the \civ\ emission line.
    The long-dashed red line is the continuum fit, with the solid orange
    line giving the overall fit. The short-dashed vertical lines gives the
    rest wavelengths of the \civ\ doublet. }
  \label{fig:QSFit-CIV}
\end{figure*}

>>>>

      {\bf The physical mechanism for the generation of the emission lines, 
        e.g., full ionization, collisional excitation or recombination, are given in

@@

While there have been many studies on triply ionised carbon, i.e.,
\civ, these have tended to focus on broad absorption line quasars
\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
\citep{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}. As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: {\it (i)} the {\it
global} (or {\it ensemble}) Baldwin effect, which is an
anti-correlation between the emission line equivalent width and the
underlying continuum luminosity of single-epoch observations of
a large number of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an individual, variable 
AGN \citep{PoggePeterson1992}. The ensemble and intrinsic Baldwin effect 
has been observed in the \civ\ broad absorption line quasar population. 
However, dramatic changes in the 
collisionally excited broad {\it emission} line of \civ\ --- and
indeed \ciii\ --- have not to this point been reported.

@@

{\bf 
Photoionization followed by recombination determines the ionization
level of carbon, and collisional excitation from the ions' ground level 
determines the line intensity. Other processes do happen 
(including radiative and three body recombination to the upper levels 
of the transition), but they are much slower unless the density is
extremely high \citep[e.g., ][and H. Netzer,
priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply ionised,
\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.

 Most of the strong lines in the rest-frame near-UV spectrum of quasars are
collisionally excited, including \ciii, C\,{\sc iv} and N\,{\sc
v}.  The \heii$\lambda$1640 recombination line is among the exceptions.
}
Details of the atomic transitions and physical mechanisms that produce
strong rest-frame UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CLQ Selection and Line Measurements}
{\bf A statistical search using optical light curves to initiate spectroscopic follow-up
  observations is proving an efficient CLQ finder, and, by design, 
our data sources and overall methodology, are in common to the recent
\citet{Ross2018}, \citet{Stern2018} and \citet{Graham2020} papers.
}

In this section we present the photometric data used to select the
CLQs and give details of the multiwavelength data where we have it.
We use optical data from the Catalina Real-time Transient Survey
\citep[CRTS;][]{Drake2009, Mahabal2011}, the Panoramic Survey
Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
Stubbs2010, Tonry2012, Magnier2013}, and the Zwicky Transient Facility
\citep[ZTF;][]{Bellm2019_ZTFOverview}. 
We also use data from the {\it WISE} mission and SDSS. 
We then give details of the spectroscopic data including emission
lines measurements.

\subsection{Photometry}
\subsubsection{Optical Photometry}
The CRTS archive\footnote{http://catalinadata.org} contains the
Catalina Sky Survey data streams from three telescopes -- the 0.7-m
Catalina Sky Survey (CSS) Schmidt and 1.5-m Mount Lemmon Survey (MLS)
telescopes in Arizona, and the 0.5-m Siding Springs Survey (SSS)
Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
with four exposures per visit, separated by 10 min. The survey
observes over 21 nights per lunation. The data are broadly calibrated
to Johnson $V$ \citep[for details, see][]{Drake2013} and the current
CRTS data set contains time series for approximately 400 million
sources to $V \sim 20$ above Declination $\delta > -30$ deg from 2003
to 2016 May (observed with CSS and MLS) and 100 million sources to $V
\sim 19$ in the Southern sky from 2005 to 2013 (from SSS). CRTS has
been extensively used to study quasar variability
\citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature, Graham2017,
Graham2020, Stern2017, Stern2018, Ross2018}.

@@

ZTF\footnote{http://ztf.caltech.edu) is a new} is a robotic 
time-domain sky survey capable of visiting the entire visible sky
north of $-$30 deg declination every night. ZTF observes the sky in
the $g$, $r$, and $i$-bands at different cadences depending on the
scientific program and sky region \citep{Bellm2019_ZTFSurveys,
Graham2019_ZTF}. The ZTF 576 megapixel camera with a 47 deg$^{2}$
field of view, installed on the Samuel Oschin 48-inch Schmidt
telescope at Palomar observatory, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30-sec exposure during new moon \citep{Masci2019}.
\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
  {figures/J1205+3422_landscape_LC.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
  {figures/J1638+2827_landscape_LC.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.20cm 0.1cm, clip]
  {figures/J2228+2201_landscape_LC.png}
  \vspace{-6pt}
  \caption[]{The light curves for the three high-redshift CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
    The timing of the spectral observations are indicated with vertical dashed lines.}
  \label{fig:civ_clqs_LCs}
\end{figure*}

\subsubsection{Mid-Infrared Photometry}
We use mid-infrared data (3.4 and 4.6$\mu$m) from the beginning
of the {\it WISE} mission \citep[2010 January; ][]{Wright2010} through
the fifth-year of {\it NEOWISE-R} operations \citep[2018 December;
][]{Mainzer2011}. The {\it WISE} scan pattern leads to coverage of the
full-sky approximately once every six months (a ``sky pass''), albeit
it with a gap between 2011 February and 2013 October when the
satellite was placed in hibernation. Hence, our light curves have a
cadence of 6 months with a 32-month sampling gap.

@@

\subsection{CLQ Selection}
{\bf As this is the first time high-redshift CLQs have been studied,
defining a formal and automatic process is not an trivial task.  Hence
we focused on a method and threshold which selects the most promising
candidates, with no claim of completeness, for visual inspection.}

Our high-redshift CLQs were identified as follows.  We selected all
64,774 SDSS DR15 sources with $z > 0.35$ classified as `quasar', that
had at least two spectra separated by $\geq 100$ days, and that had a
corresponding CRTS light curve. We fitted a damped random walk to the
CRTS data via Gaussian process regression (using the
\href{https://gpy.readthedocs.io/en/deploy/}{GPy Python} library).
{\bf This allowed us to predict the photometric magnitudes and their
uncertainties at the epochs of the SDSS spectra for each source
\citep[see][]{Rasmussen_Williams2006}.} Candidate objects with
$|\Delta V| > 0.3$ magnitude were then selected for visual
inspection. {\bf This corresponds to at least a 33\% change in flux
between the two epochs. Approximately 1\% of quasars should show this
level of variability over the timescales considered
\citep{Graham2017}.}

@@

Proper comparison of the spectra requires reliable flux calibrations,
which is a challenge since not all data were taken in photometric
conditions.  SDSS spectra are spectrophotometrically calibrated.  BOSS
and eBOSS spectra have spectrophotometric corrections applied in the
latest data release \citep{Hutchinson2016, Jensen2016, Margala2016}.
However, some of the Palomar and Keck data suffered from variable
conditions and clouds.  For lower redshift AGN, the narrow \oiii
emission line is typically used to align spectrophotometry since it is
spatially extended and not expected to change significantly on human
timescales \citep[e.g.,][]{Barth2011}. However, due to the
high-redshift of our quasars, \oiii is not available to us for
scaling the spectra.  Instead, we use photometric data from ZTF
since our Palomar and Keck data were all taken after MJD 57500.  This
provides broad-band photometry at the time of the spectroscopy, which
we use to scale the spectra whose initial calibration is based on
spectrophotometric standards observed on the same nights.  {\bf We 
  estimate the resulting uncertainty in flux calibration is $\sim$5\%.
  This uncertainty is not propagated into measurements.}

@@

In particular, we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and EWs of 20 emission
lines, including \civ, C\,{\sc iii}], and {Mg\,{\sc ii}}. We process and fit
all nine spectra (3 quasars with 3 epochs) using the lastest version
(v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, as is the case for all
our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.

{\bf As described in \citet{Calderone2017}, the uncertainties in the
measured quantities are determined by two methods: a Fisher matrix
method and a Monte Carlo resampling method.  One might expect
correlations among model parameters, e.g. emission-line luminosities
and widths, potentially causing the Fisher matrix method to
underestimate the errors.  However, upon investigation, the parameters
of the involved model components (a power-law for the continuum and a
single Lorentzian profile for the emission lines) show negligible
correlations. Therefore, we use the Fisher matrix method to estimate
the uncertainties on the model parameters.  Section 2.8.3 and Appendix
B4 of \citet{Calderone2017} gives further details and compares the
Fisher matrix and Monte Carlo resampling uncertainties and
distributions.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
curves for three high-redshift CLQ quasars.
%%
Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for
SDSS J1205+3422.  For J1205+3422, our spectral observations cover 5195
observed days, corresponding to 1691 days in the rest-frame. This
quasar was initially identified in SDSS in 2005 May as a bright, $g
\approx 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv},
\civ, C\,{\sc iii}], and Mg\,{\sc ii} emission.  \civ\ has a blueshift of
$\approx$580$\pm$80 km s$^{-1}$.  By 2019, however, the optical
brightness dropped by nearly 2 magnitudes and the spectra are
significantly less blue.  \lya and \nv are detectable in both 2019
spectra, but is just blueward of the wavelength range covered by the
original SDSS spectrum. The \civ\ and \ciii\ lines have faded
significantly between the SDSS observation in 2005 and the Palomar
observations in 2019.  Note that \civ\ is extremely faint in the 2019
February spectrum (MJD 58538), but that night suffered from poor conditions.

Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for
SDSS J1638+2827.  For J1638+2827, our spectral observations cover 4030
observed days, corresponding to 1265 days in the rest-frame. Here, in
the initial epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
iii}]. However, $\approx$400 rest-frame days later, the broad \civ\ and
\ciii\ emission lines have faded, the continuum slope around 1400\AA\
has changed from $\approx-1.16$ to $\approx-2.17$, but the \lya/\nv
emission complex is very similar in shape {\bf and intensity}. Around
870 days in the rest-frame after the second spectral epoch, at the
time of the third spectral epoch, the source has brightened from
optical magnitudes of $\sim$20 mag to $\sim$18.5 mag. Ly$\alpha$,
N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
\mgii\ being seen for the first time at high signal-to-noise. An
absorption feature between \lya and \nv is seen in all three spectral
epochs.

Figure~\ref{fig:civ_clqs_J22_spec} shows the rest-frame spectra for
SDSS J2228+2201.  For J2228+2201, our spectral observations cover 2504
observed days, corresponding to 778 days in the rest-frame. Over the
course of 240 rest-frame days, \civ\ and \ciii\ both {\it emerge} as
BELs and {\bf the standard UV/blue continuum becomes stronger.}  Then,
over the course of 538 days in the rest-frame, the broad emission,
while still very present, reduces in line flux and the UV/blue continuum
diminishes.  However, the third epoch still corresponds to a source
more luminous than the initial BOSS spectrum.

\begin{figure*}
  \centering
  \includegraphics[width=18.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit models of the \civ\ spectral region.
    The solid blue line is the Lorentzian profile fit to the \civ\ emission line.
    The long-dashed red line is the continuum fit, with the solid orange
    line giving the overall fit. The short-dashed vertical lines give the
    rest wavelengths of the \civ\ doublet. }
  \label{fig:QSFit-CIV}
\end{figure*}
